
# Section I {.unnumbered}

```{r, include=FALSE, warning=F}

fetch_records <- c('section_i', 'section_h')

source('../utils/import-data.R')

ref_i02_freq <- data.frame(
  i02_freq = c(1:5),
  i02_freq_m = c(365, 52, 24, 12, 1)
)

section_h <- hpq$section_h %>% 
  select(case_id, h6_cfincome) %>% 
  collect()

section_i <- hpq$section_i %>% 
  select(-matches('specify')) %>% 
  collect() %>% 
  inner_join(section_h, by = 'case_id') %>% 
  left_join(ref_i02_freq, by = 'i02_freq')
  
```

### I01 - Usual or average expenditure is blank or invalid

Usual or average expenditure should not be blank or invalid

```{r, echo=F, warning=F, error=F}
(
  cv_i01_usualexp_blnk <- section_i %>% 
    filter(is.na(i01_foodconsump) | i01_foodconsump <= 0) %>% 
    select_cv(i01_foodconsump, h = 'i01_foodconsump')
)[[1]]
```


### I02 - Multiplier for frequency is blank or invalid

Multiplier for frequency should not be blank and answer must be in the value set.

```{r, echo=F, warning=F, error=F}
(
  cv_i02_freq_vlst <- section_i %>% 
    filter(!(i02_freq %in% c(1:5))) %>% 
    select_cv(i02_freq, h = 'i02_freq')
)[[1]]
```


### I03 - Expenditure on food consumed occasionally is blank or invalid

Expenditure on food consumed occasionally should not be blank or invalid.

```{r, echo=F, warning=F, error=F}
(
  cv_i03_occexp_blnk <- section_i %>% 
    filter(is.na(i03_expenditure) | i03_expenditure < 0) %>% 
    select_cv(i03_expenditure, h = 'i03_expenditure')
)[[1]]
```


### I04 - Total food inconsistent with the sum of individual food consumption
  
Total annual food consumption should be consistent with the sum of the expenditure on food consumed occassionally and the product of the usual/average expenditure and the multiplier for frequency.

```{r, echo=F, warning=F, error=F}
(
  cv_i04_totalfoodcnsmptn_vlst <- section_i %>% 
    filter_at(vars(matches('i0[1-4]._*')), all_vars(!is.na(.))) %>%
    filter((i01_foodconsump * i02_freq_m) + i03_expenditure != i04_totalfood) %>% 
    select_cv(matches('i0[1-4]._*'))
)[[1]]
```

### I04 - Invalid answer in total annual food consumption
  
Total annual food consumption should be greater than zero.

```{r, echo=F, warning=F, error=F}
(
  cv_i04_totalfoodcnsmptn_missing_o <- section_i %>% 
    filter(is.na(i04_totalfood) | i04_totalfood <= 0) %>%
    select_cv(i04_totalfood, h = 'i04_totalfood')
)[[1]]
```

### I04 - Total annual food consumption is greater than family income

Total annual food consumption should be less than family income. 

```{r, echo=F, warning=F, error=F}
(
  cv_i04_totalfoodcnsmptn_blnk <- section_i %>% 
    filter(!is.na(i04_totalfood), !is.na(h6_cfincome), i04_totalfood >= h6_cfincome) %>% 
    select_cv(i04_totalfood, h6_cfincome, h = c('i04_totalfood', 'h6_cfincome'))
)[[1]]
```



```{r, include=F, echo=F, warning=F, error=F}

validation_section_i <- as_tibble(ls(pattern = '^cv_i')) %>% 
  mutate(cases = map(.$value, function(x) { eval(as.name(x))[[2]] })) %>% 
  unnest(cases) 

save(validation_section_i, file = '../data/validation/validation_section_i.Rdata')

```

